\documentclass[11pt]{article}

\usepackage[a4paper, hmargin=15mm, vmargin=17mm, top=20mm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}

\raggedright
\raggedbottom
\setlength{\tabcolsep}{0mm}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\titleformat{\section}{
    \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule]

\newcommand{\cvheading}[3]{
    \begin{tabular*}{0.9\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\\
        \textit{#2} & \textit{#3}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\cvitem}[1]{\item #1\vspace{-2pt}}

\overfullrule=2cm

\usepackage[T1]{fontenc}
\usepackage[urw-garamond]{mathdesign}

% -----------
% CV DOCUMENT
% -----------
\begin{document}

% ------
% HEADER
% ------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Charles Mita}\\
%ADDRESS_STREET\\
ADDRESS_STREET & Email: \href{mailto:ADDRESS_EMAIL}{ADDRESS_EMAIL}\\
ADDRESS_TOWN & Mobile: CONTACT_MOBILE\\
ADDRESS_POSTCODE & GitHub: \href{https://GITHUB_URL}{GITHUB_URL}\\
\end{tabular*}

%--------
% SUMMARY
%--------
\section{Profile}
\begin{itemize}
    \cvitem
        {Result focused and conscientious Software Developer with 6 years experience in the
        Scientific Research sector and experience within the online Credit sector, currently
        working on Google's build system Blaze and its open source counterpart Bazel.}
    \cvitem
        {Most experienced with Java and Python application development with exposure to
        C, C++ development, and experience with C\# and VB.NET web development.}
\end{itemize}
%-----------
% EXPERIENCE
%-----------
\section{Experience}
\begin{itemize}
    \item
        \cvheading
            {Google}
            {Software Engineer for Bazel and Blaze (Build Rules)}{Dec. 2019 - Present}
            \begin{itemize}
            \cvitem
                {Development and improvements of the language rules for the Bazel and Blaze build systems,
                focusing of the C++ and Go languages.}
            \cvitem
                {Improvements to Blaze/Bazel's coverage collection, supporting mergring of coverage reports and
                adding support for Jacoco's filters for Java coverage collection.}
            \end{itemize}
    \item
        \cvheading
            {Diamond Light Source Ltd.}
            {Software Developer in Data Acquisition}{Jan. 2014 - Nov. 2019}
            \begin{itemize}
            \cvitem
                {Development and maintenance of the
                \href{https://github.com/openGDA}{Data Acquisition framework (GDA)}, an open source Java project.}
            \cvitem
                {Design and development of the data acquisition system for an automated X-ray beamline for
                Macromolecular X-ray crystallography (VMXi).}
            \cvitem
                {Design and development of a Python project
                (\href{https://github.com/dls-controls/scanpointgenerator}{scanpointgenerator})
                to efficiently describe and produce positions for n-dimensional scans for X-ray data collections.}
            \cvitem
                {Design and development of a C plugin for a data analysis tool to allow efficient processing of datasets
                collected from the latest high speed X-ray detectors (1-100 GB datasets).}
            \cvitem
                {Support for data acquisition on multiple X-ray beamlines; including integration and control of devices
                (motors, detectors, spectrum analysers, and other hardware) into the data acquisition framework.}
            \end{itemize}
    \item
        \cvheading
            {Credit Reporting Agency Ltd.}
            {Software/Web Developer}{June 2012 - Dec. 2013}
            \begin{itemize}
            \cvitem
                {Maintenance of multiple customer facing websites using VB.NET.}
            \cvitem
                {Rewriting of the website aimed at Australian consumers to match the services
                offered to UK consumers.}
            \end{itemize}

\end{itemize}

%----------
% EDUCATION
%----------
\section{Education}
\begin{itemize}
    \item
        \cvheading
            {University of Warwick}
            {B.Sc Maths and Physics 2:1}{Oct. 2009 - July 2012}
    \item
        \cvheading
            {Truro College}
            {A levels in Maths, Further Maths, Physics, Chemistry (AAAA)}{Sept. 2007 - July 2009}
\end{itemize}


%-------
% SKILLS
%-------
\section{Skills}
\begin{description}[style=nextline]
    \item[Technologies:]
            Experience with Java, Python, C, Git, ASP.NET, VB.NET, HDF5.\\
            Working knowledge of C++, C\#, SVN, GDB, Javascript.
    \item[Operating Systems:]
        {Windows, Linux}
\end{description}

\end{document}
